---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fritzlog

<!-- badges: start -->
<!-- badges: end -->

`fritzlog` is a package to analyse device login activity for a FritzBox WiFi router. It can:

* Load a log file and transform into a well-formatted tibble with `fritz_log()`
* Load a log file and create a graphical summary of device login activity with `fritz_plot()`

## Installation

You can install the development version of fritzlog from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nbostelmann/fritzlog")
```

## How to create a log file

Go to the [FritzBox admin page](http://fritz.box/). In the main menu select `System > Ereignisse > WLAN > Druckansicht` and copy & paste the output to a text file.

An example file is included with this package.

```{r}
file <- system.file("extdata", "fritz.log", package = "fritzlog", mustWork = TRUE)

readr::read_lines(file, n_max = 15)
```

## fritz_log()

Simply call `fritz_log()` with the path to the log file to get a well-formatted tibble of device login activity which can be used for further analysis. The function has no other parameters.

```{r}
library(fritzlog)

fritz_log(file)
```

## fritz_plot()

`fritz_plot()` can summarise device login activity in a histogram or a frequency polygon plot in `ggplot2` format. It takes the path to the log file and the plot type as parameters.

### Histogram

Call `fritz_plot()` with `plot_type = "histogram"`.

```{r fig.width=10}
fritz_plot(file, plot_type = "histogram")
```

### Frequency polygon

Call `fritz_plot()` with `plot_type = "freqpoly"`.

```{r fig.width=10}
fritz_plot(file, plot_type = "freqpoly")
```

### Both in one

Plots can be easily combined, for example with the `patchwork` package.

```{r fig.width=10}
library(patchwork)

fritz_plot(file, plot_type = "histogram") /
  fritz_plot(file, plot_type = "freqpoly")
```
